\documentclass[letterpaper,11pt]{extarticle}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{phonenumbers}
\usepackage{fontawesome5}
\usepackage{hyperref}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}
{\vspace{-6pt}\scshape\raggedright\large}
{}{0em}{}[\titlerule \vspace{-6pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small#4}
\end{tabular*}
}
\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small\textbf{#1} & \small #2
\end{tabular*}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep,topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\definecolor{lightgray}{RGB}{150, 150, 150}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {{\Huge \scshape \textbf{SAMIM REZA}} \\[4pt]
    \textcolor{lightgray}{
        \faPhone\ +8801747773315 \quad
        \faEnvelope\ \href{mailto:samimreza2111@gmail.com}{samimreza2111@gmail.com} \quad
        \faMapMarker\ Dhaka, Bangladesh \\[2pt]
        \faLinkedin\ \href{https://linkedin.com/in/samim-reza}{linkedin.com/in/samim-reza} \quad
        \faGithub\ \href{https://github.com/samim-reza}{github.com/samim-reza} \quad
        \faGlobe\ \href{https://samim-reza.github.io}{samim-reza.github.io}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Green University of Bangladesh}{2022 -- 2025}
{B.Sc. in Computer Science and Engineering}{CGPA: 3.80/4.00}
\resumeSubheading
{Government Bangabandhu College}{2017 -- 2019}
{Higher Secondary Certificate}{GPA: 4.75/5.00}
\resumeSubheading
{S. M. Model Govt. High School}{2012 -- 2017}
{Secondary School Certificate}{GPA: 5.00/5.00}
\resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeProjectHeading
{Machine Learning Engineer — Brandifies}{Feb 2025 -- Present}
\resumeItemListStart
\resumeItem{Built end-to-end ML pipelines: data preprocessing, feature engineering, model training, and evaluation}
\resumeItem{Fine-tuned LLMs and implemented RAG-based chatbot systems with vector databases}
\resumeItem{Developed predictive models using XGBoost and similar boosting algorithms}
\resumeItemListEnd

\resumeProjectHeading
{Robotics Engineer Intern — RoboTech Valley}{Jul -- Sept 2025}
\resumeItemListStart
\resumeItem{Designed robotics modules using embedded systems and ROS for autonomous navigation.}
\resumeItemListEnd

\resumeProjectHeading
{Teaching Assistant — Green University of Bangladesh}{May -- Aug 2025}
\resumeItemListStart
\resumeItem{Conducted demo classes on C Programming and Data Structures.}
\resumeItem{Evaluated exam scripts and prepared grade sheets.}
\resumeItemListEnd

\resumeProjectHeading
{Programming Trainer — Green University of Bangladesh}{Jan -- Dec 2025}
\resumeItemListStart
\resumeItem{Trained students for competitive programming through weekly problem-solving sessions.}
\resumeItemListEnd

\resumeProjectHeading
{Mentor — University Mentorship Program}{Jun 2023 -- Aug 2025}
\resumeItemListStart
\resumeItem{Mentored first-year students in programming fundamentals and professional tools.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------RESEARCH-----------


\section{Research}

\resumeSubHeadingListStart
\resumeProjectHeading
{Edge Detection for Smoke-Degraded Images using Fractional Derivative (Published)}{2026}
\resumeItemListStart
\resumeItem{Proposed a fractional calculus-based edge detection operator achieving robust boundary
extraction under smoke and haze degradation conditions.}
\resumeItemListEnd
\resumeSubHeadingListEnd
% \textbf{Ongoing} \textit{\small(2 submitted)}
\resumeSubHeadingListStart
\resumeProjectHeading
{Denoising Diffusion Probabilistic Models}{}
\resumeItemListStart
\resumeItem{Integrating edge detection for enhanced image generation.}
\resumeItemListEnd

\resumeProjectHeading
{Federated Learning}{}
\resumeItemListStart
\resumeItem{Adaptive client selection algorithms for optimal convergence.}
\resumeItemListEnd

% \resumeProjectHeading
% {Human-in-the-Loop ML}{}
% \resumeItemListStart
% \resumeItem{Survey on HITL approaches in modern ML systems.}
% \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\small{
\textbf{Languages}: C, C++, Python, Java, JavaScript, PHP \\
\textbf{AI/ML}: PyTorch, TensorFlow, Scikit-learn, LangChain, VectorDB, RAG, LLM, Roboflow \\
\textbf{Web/Backend}: Django, FastAPI, React, REST APIs, PostgreSQL, MySQL, PWA \\
\textbf{Tools \& Platforms}: ROS, Git, Docker, Celery, Redis, Meta Graph API, Linux, LaTeX, Render, Azure, Arduino, Raspberry Pi, Jetson, ESP32
}

%-----------FEATURED PROJECTS-----------
\section{Featured Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{TrueDoc — Django, React, DRF, SimpleJWT, PostgreSQL, QR}{\href{https://github.com/samim-reza/TrueDoc}{GitHub}}
\resumeItemListStart
\resumeItem{Saas for digital document attestation in Bangladesh with QR-backed verification, role-based access (citizen/verifier/org), JWT auth, and BDT payment model}
\resumeItemListEnd

\resumeProjectHeading
{GoUp — Django, Celery, Redis, Meta Graph API, Twilio}{\href{https://github.com/samim-reza/GoUp}{GitHub}}
\resumeItemListStart
\resumeItem{For Lead Ads automation; syncs pages/forms via Meta API, webhooks, triggers SMS follow-ups Celery \& Redis}
\resumeItemListEnd

\resumeProjectHeading
{Personal AI Assistant — LLM, RAG, LangChain}{\href{https://samim-chatbot-app.azurewebsites.net/}{Live} $\vert$ \href{https://github.com/samim-reza/MyChatBot}{GitHub}}
\resumeItemListStart
\resumeItem{Built an LLM-powered chatbot with retrieval-augmented generation for personalized assistance.}
\resumeItemListEnd

\resumeProjectHeading
{KobitaLM — Bengali Poetry Generator}{\href{https://huggingface.co/samim-reza/KobitaLM}{Model} $\vert$ \href{https://github.com/samim-reza/KobitaLM}{GitHub}}
\resumeItemListStart
\resumeItem{Fine-tuned Gemma 2 9B with LoRA and RAG for Bengali poetry generation.}
\resumeItemListEnd

\resumeProjectHeading
{WeCare Medical Service App — FastAPI, Qwen3-VL, PWA}{\href{https://github.com/samim-reza/FutureBuilders2025_GreenU_Tensors}{GitHub}}
\resumeItemListStart
\resumeItem{Developed an offline-first PWA for rural healthcare with AI-assisted triage capabilities.}
\resumeItemListEnd

\resumeProjectHeading
{Cirrhosis Outcome Prediction — XGBoost, LightGBM, CatBoost}{BAIC 2025}
\resumeItemListStart
\resumeItem{Built an ensemble ML classifier with 55 engineered features, achieving 14.5\% accuracy gain.}
\resumeItemListEnd

\resumeProjectHeading
{Hasib Academic System — Django, PostgreSQL, Render, Gunicorn}{\href{https://hasibislamicacademy.github.io/}{Live} $\vert$ \href{https://github.com/samim-reza/Hasib_School}{GitHub}}
\resumeItemListStart
\resumeItem{A production-ready Django application for school workflows including admissions, student
attendance, notices, teacher accounts, and finance tracking with PDF export.
Tailored for Bangla-speaking users.}
\resumeItemListEnd

\resumeProjectHeading
{Union Ledger — Django, PostgreSQL, Render}{\href{https://samim-reza.github.io/union}{Live} $\vert$ \href{https://github.com/samim-reza/union}{GitHub}}
\resumeItemListStart
\resumeItem{Built a collaborative financial tracking web app with consensus-based voting for deposits,
loans, repayments, and investments.}
\resumeItemListEnd

\resumeProjectHeading
{Mars Rover — ROS, Embedded Systems}{\href{https://github.com/samim-reza/Rover-robot}{GitHub}}
\resumeItemListStart
\resumeItem{Developed a ROS-based autonomous navigation system for Mars rover simulation.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------COMPETITIVE PROGRAMMING-----------
\section{Competitive Programming}
\resumeItemListStart
\resumeItem{Champion: Intra Dept Programming Contest 2024.}
\resumeItem{3x ICPC Regionalist: 2022, 2023, 2024.}
\resumeItem{Around 1000 problems solved across online judges.}
\resumeItem{Kaggle Competitor: Active in ML competitions.}
\resumeItem{Problem Setter: Junior Programming Contests.}
\resumeItem{Participated: NCPC 2023, IUPC 2023/2024.}
\resumeItemListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\resumeItemListStart
\resumeItem{Vice Chancellor's and Dean's Award for Academic Excellence.}
\resumeItem{Champion, Inter Dept Programming Contest 2024.}
\resumeItem{Secured 8th position in BUBT Artificial Intelligence Conquest (Kaggle).}
\resumeItem{National IT Quiz Competition Medalist.}
\resumeItemListEnd

%-----------REFERENCES-----------
\section{References}

\begin{multicols}{2}
\textbf{Prof. Dr. Md. Saiful Azad} \\
Dean, Faculty of Science \& Engineering \\
Green University of Bangladesh \\
Email: dean@fse.green.edu.bd \\
Mobile: +880 1747-230418

\columnbreak

% \vspace{6pt}
\textbf{Ms. Umme Ruman} \\
Assistant Professor \\
Green University of Bangladesh \\
Email: ruman@cse.green.edu.bd \\
Mobile: +880 1799-089667
\end{multicols}

\end{document}